Vragenlijst thesis evaluatie

### 2015-02-23 doc/template/chap-4.tex
Matrixen vervolg commit

  \path (A) edge              node {} (B)
            edge              node {} (D)
        (B) edge              node {} (A)
        	edge			  node {} (C)
        (C) edge              node {} (B)
            edge 			  node {} (D)
            edge			  node {} (E)
            edge			  node {} (F)
        (D) edge 			  node {} (C)
            edge              node {} (A)
        (E) edge 			  node {} (C)
    	(F)	edge			  node {} (C);
\end{tikzpicture}
\\
%\[
%\begin{bmatrix}
%    x_{11}       & x_{12} & x_{13} & \dots & x_{1n} \\
%    x_{21}       & x_{22} & x_{23} & \dots & x_{2n} \\
%    \hdotsfor{5} \\
%    x_{d1}       & x_{d2} & x_{d3} & \dots & x_{dn}
%\end{bmatrix}
%=
%\begin{bmatrix}
%    x_{11} & x_{12} & x_{13} & \dots  & x_{1n} \\
%    x_{21} & x_{22} & x_{23} & \dots  & x_{2n} \\
%    \vdots & \vdots & \vdots & \ddots & \vdots \\
%    x_{d1} & x_{d2} & x_{d3} & \dots  & x_{dn}
%\end{bmatrix}
%\] 
The adjacent matrix becomes this matrix $A$: \\

@@

Matrix $A \times A = A^{2}$ becomes the matrix with the number of paths with 2 steps from $N_{i}$ to $N_{j}$:\\

@@

Matrix $A^{2} \times A = A^{3}$ becomes the matrix with the number of paths with 3 steps from $N_{i}$ to $N_{j}$:\\

@@

With this knowledge we can calculate in how many steps a node is infected. $A$ calculates which nodes are infected after 1 step, $A^{N}$ calculates which nodes are infected in N steps.. So if we want to know how many nodes are infected after 3 steps we have to add every matrix $(A + A^{2} + A^{3}) $ and see which entry is a non zero entry. 
\end{document}

>>>>

  \path (A) edge              node {} (B)
            edge              node {} (D)
        (B) edge              node {} (A)
        	edge			  node {} (C)
        (C) edge              node {} (B)
            edge 			  node {} (D)
            edge			  node {} (E)
            edge			  node {} (F)
        (D) edge 			  node {} (C)
            edge              node {} (A)
        (E) edge 			  node {} (C)
    	(F)	edge			  node {} (C);
\end{tikzpicture}
\\
%\[
%\begin{bmatrix}
%    x_{11}       & x_{12} & x_{13} & \dots & x_{1n} \\
%    x_{21}       & x_{22} & x_{23} & \dots & x_{2n} \\
%    \hdotsfor{5} \\
%    x_{d1}       & x_{d2} & x_{d3} & \dots & x_{dn}
%\end{bmatrix}
%=
%\begin{bmatrix}
%    x_{11} & x_{12} & x_{13} & \dots  & x_{1n} \\
%    x_{21} & x_{22} & x_{23} & \dots  & x_{2n} \\
%    \vdots & \vdots & \vdots & \ddots & \vdots \\
%    x_{d1} & x_{d2} & x_{d3} & \dots  & x_{dn}
%\end{bmatrix}
%\] 
The adjacent matrix becomes this matrix $[A]$: \\

@@

Matrix $A \times A = A^{2}$ becomes the matrix with the number of paths with 2 steps from $N_{i}$ to $N_{j}$: We denote this matrix as matrix \textit{[B]}\\

@@

Matrix $A^{2} \times A = A^{3}$ becomes the matrix with the number of paths with 3 steps from $N_{i}$ to $N_{j}$: We denote this matrix as matrix \textit{[C]}\\

@@

With this knowledge we can calculate in how many steps a node is infected. $A$ calculates which nodes are infected after 1 step, $A^{N}$ calculates which nodes are infected in N steps.. So if we want to know how many nodes are infected after 3 steps we have to add every matrix $(A + A^{2} + A^{3}) $ and see which entry is a non zero entry.

\end{document}
